Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-17 talk/dls2012/paper.tex
describe control dependencies

>>>>

It is interesting to note that the described approach automatically deals with
implicit control dependencies correctly, whereas in other approaches this needs
to be carefully programmed in. A commonly used example for a control dependency
is a division operation that needs to be preceded by a check for the second
argument being 0. In a trace, such a check would be done with a guard. The
division operation must not be moved before that guard, and indeed, this is
never done. If the division is loop invariant, the result computed in copy of
the division operation in the preamble is reused. This division operation is
preceded by a copy of the non-null guard, which ensures that it can be executed
correctly.
